Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
ok

## Global knowledge production and large-scale library catalogues

@@

**Data: bibliographic catalogues 1640-1828**

@@

- **Parsers** From original MARC/XML to CSV to RData

- **Preprocessing** Cleaning up the fields.

```{r}
library(bibliographica)
polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
polish_place("Sur l'imprimea londres")
```

**Analysis**

```{r}
library(knitr)
kable(as.data.frame(top(df0, "publication_place", 3)))
```

**Visualization**

```{r, fig.width=10, fig.height=7}
titlecount_timeline(subset(df0, catalog == "Fennica"), 
                         "publisher", nmin = 500, mode = "n")$plot
```

>>>>

## Global knowledge production and massive library catalogues

@@

### Data: bibliographic catalogues 1640-1828

@@

**Parse** From original MARC/XML to CSV to RData

**Preprocess** Cleaning up the fields.

```{r, message=FALSE, warning=FALSE}
polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
polish_place("Sur l'imprimea londres")
```

**Enrich**

```{r, message=FALSE, warning=FALSE}
get_country("Porvoo")
```

**Analyse**

```{r, message=FALSE, warning=FALSE}
library(knitr)
kable(as.data.frame(top(df0, "publication_place", 3)))
```

**Visualize**

```{r, fig.width=10, fig.height=7, message=FALSE, warning=FALSE}
titlecount_timeline(subset(df0, catalog == "Fennica"), 
                         "publisher", nmin = 500, mode = "n")$plot
```
